---
title: "homework-2"
author:
- name: Jay Agustin
  affiliation: NC State University
  email: alagusti@ncsu.edu
format: pdf
editor: visual
---

## Question 1

```{r}
#| eval: false

install.packages("aRtsy")
```

The function “install.packages()” lets you download pre-made functions and datasets for use in future sessions. Once you install them, you won’t need to do it again.

The function “library()” loads the installed package in your current R session. It’s similar to checking the box next to the package you want to use in the Packages tab. You might want to dedicate a code chunk to all the packages you'll use so your document renders properly.

\newpage

# Packages

## Question 2

```{r}
library(aRtsy)
```

Collatz Conjecture:

$$f(n) = \begin{cases} 
      \frac{n}{2} & \text{if } n = 0 \ (\text{mod}\ 2) \\
      \frac{3n + 1}{2} & \text{if } n = 1 \ (\text{mod}\ 2)
   \end{cases}$$
   
The Collatz conjecture, or the $3n+1$ problem, claims that no matter which positive integer you start with, you will eventually reach 1. 

\newpage

## Question 3

#### a) Canvas_collatz()

```{r}
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```

This ggplot shows how many steps (or the general path) it takes for a set of starting integers ($n = 10$) to reach 1. It’s made to be plotted in blue.

#### b) Different Output?



